### 2015-07-05 narrative/intro.tex
editing of intro

This forced the team to decide which pieces of data to save from the large amount of data; in 
other words, they had to prioritize which were the most important pieces and save only those. They had to further break down the still large data into two categories, data which they thought they would touch after one or two days of runs are completed and after the whole simulation is going to be completed (after ten days of runs), and what they would do with these different categories of data (the access pattern of the large data).

They then had to develop new application specific data reduction techniques, and encode that into the application code itself on top of ADIOS, the middleware I/O layer. They then had to implement a crude discovery system to understand
which pieces of data were stored on the parallel file system and which pieces were on tape, and also which pieces were moved over to PPPL for immediate analysis by the user.

This solution worked well for the first day of run but after the second day more problems occurred: the variability in the time that it took to write the data made the I/O prohibitively expensive, because even though the project had reserved the majority of the resources at the OLCF, the file system was shared and sometimes the writing time took less 100 seconds, and at other times it was over 1,000 seconds. There was no method for the application or the user to monitor and predict this resource usage and to dynamically adapt to write less data when the I/O time was going to be longer. The greatest problem, however, comes after the simulation   completes: even to visualize the reduced data, just to get a first look at the visualization data, it could take over a month because some of the timesteps will be on tape and other timesteps will be on the file system. There is no method to just look at the data quickly at some level of quality quickly and understand which regions of the simulation to focus on in more detail.

>>>>

This forced the team to carefully scrutinize the large amount of data to be generated and save only the very most important pieces. Further, they had to break this greatly reduced data into two categories: first data they thought they would need to access while the simulation was running or shortly thereafter, and second data they would need after the simulation was finished. The former category would be stored on disk, and the later would be archived. Additionally, they needed to figure out how to efficiently retrive these different categories of data for post-processing, analysis and visualization.

Finally, the team had to develop new application specific data reduction techniques and encode them into the ADIOS middleware I/O layer. In order to do this, they had to implement a rudimentary discovery system to determine which data were located on disk, and which were on tape archive.  Additionally, some pieces of data needed to be moved to PPPL for immediate analysis.

This solution worked well for the first day of the run but after the second day significant problems occurred: I/O variability became prohibitively expensive. Although the team had reserved resources for the run, the file system was shared, and a 10X variability in I/O speeds was observed. What is needed for this problem is a system to monitor, predict and manage resource usage in a dynamically adaptable way. Such a system could write more data when the resource is idle, and less data when it is very busy.

However, the most significant problem occurs after the simulation run completes. Basic visualizations from the reducted data, just to get a high-level view of the simulation, can take significant time. While some timesteps might be on disk, others are archived on tape (where transfer could take weeks). Further, visualization of detailed views of the simulation are even more complicated.
